---
title: "Prophet_stock_price"
output: 
  html_document:
    toc: true
    toc_depth: 3
---

# webpage catalogue

[Prophet](https://www.r-bloggers.com/prophet-how-facebook-operationalizes-time-series-forecasting-at-scale/ "Prophet how to")

[Forecasting at Scale](https://facebookincubator.github.io/prophet/static/prophet_paper_20170113.pdf)

[Prophet for stock price](https://msperlin.github.io/2017-03-05-Prophet-and_stock-market/)


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# set working directory
rm(list = ls(all.names = T))
```

# package difference

```{r, eval=FALSE}
library(BatchGetSymbols)
library(quantmod)

my.stocks  <- c('AAPL')
first.date <- as.Date('2015-01-01')
last.date <- Sys.Date() # 現在の日時取得
# data.frame形式になる
df.stocks <- BatchGetSymbols(my.stocks, 
                             first.date = first.date, 
                             last.date = last.date)[[2]]
#xts形式になる,ticker列,時間列がない
df.stocks_2 <- getSymbols(Symbols = my.stocks, 
                          from=first.date, 
                          to=last.date, 
                          auto.assign = FALSE)
```

# library package 

```{r, message = FALSE}
library(BatchGetSymbols)
library(prophet)
library(ggplot2)
library(zoo)
library(lattice)
library(dplyr)
library(broom)
```

```{r}
#road data
load("C:/Users/SHIO-160412-4/Desktop/R_prophet/data/SP500.RData")
dim(df.stocks)
tail(df.stocks)
```

```{r, eval=FALSE}
# 乱数シード
set.seed(15)
# number of stocks
n.stocks <- 30

# unique:文字抽出
my.stocks <- sample(unique(df.stocks$ticker), n.stocks)

# 対象のデータのみ使う
df.stocks <- df.stocks[df.stocks$ticker %in% my.stocks, ]
```

```{r, eval=FALSE}
# example
# 100個の乱数+100日分の時系列
df.est <- data.frame(y = rnorm(100), ds = Sys.Date() + 1:100)

m <- prophet(df = df.est)
```

# prophet function

```{r}
est.model.and.forecast <- function(df.in, nfor){
  # Estimated model using prophet and forecast it
  #
  # Args:
  #   df.in - A dataframe with columns price.adjusted and ref.date
  #   nfor - Number of out-of-sample forecasts
  #
  # Returns:
  #   A dataframe with forecasts and errors for each horizon.
  
  require(prophet)
  require(dplyr)
  
  my.ticker <- df.in$ticker[1]
  
  #cat('\nProcessing ', my.ticker)
  
  # calculation return per
  df.in$ret <- with(df.in, c(NA,diff(log(price.adjusted))))
  
  # extract date and return per
  df.in <- select(df.in, ref.date, ret)
  names(df.in) <- c('ds', 'y')
  
  # num of the training
  idx <- nrow(df.in) - nfor
  
  # training data
  df.est <- df.in[1:idx, ]
  # test data
  df.for <- df.in[(idx + 1):nrow(df.in), ]
  
  # all out put change for character
  capture.output(
    m <- prophet(df = df.est)
  )
  
  # forecast 50 days ahead (it also includes non trading days)
  df.pred <- predict(m,
                     make_future_dataframe(m,
                                           periods = nfor + 50))
  
  #### 土日も含めて予測して、その後元データと日付が一致している部分のみ取り出している
  # merge real num and predict num
  df.for <- merge(df.for, df.pred, by = 'ds')
  df.for <- select(df.for, ds, y, yhat)
  
  # forecast statistics
  df.for$eps <- with(df.for,y - yhat)
  df.for$abs.eps <- with(df.for,abs(y - yhat))
  df.for$perc.eps <- with(df.for,(y - yhat)/y)
  df.for$nfor <- 1:nrow(df.for)
  df.for$ticker <- my.ticker
  
  return(df.for)
}
```

```{r}
# 関数をtickerごとに繰り返す
# リスト形式で返される
out.l <- by(data = df.stocks,
            INDICES = df.stocks$ticker, 
            FUN = est.model.and.forecast, nfor = 30)

# 縦にマージする
my.result <- do.call(rbind, out.l)
```

# ggplot

```{r}
# abs.eps:difference of real num and predict num 
p <- ggplot(my.result, aes(x=factor(nfor), y=abs.eps))
p <- p + geom_boxplot()

print(p)
```

# profit rate function

```{r}
profit_rate_func <- function(my.result){
  # extract ticker
  my.ticker <- my.result$ticker[1]

  # extract date, y, yhat
  my.result_return <- select(my.result, y , yhat) %>% as.zoo()
  # get profit rate
  my.result_profit <- apply(my.result_return, 2, function(i) log(cumprod(1 + i))) %>% as.zoo()
  # input date
  index(my.result_profit) <- my.result[,1] 
  #plot
  profit_plot <- 
    xyplot( 
    my.result_profit,
    main = paste("stock name :", my.ticker, sep = ""),
    superpose=T,
    col=c("darkred", "darkblue"),
    lwd=2,
    key=list( 
      text=list(
        c("real number", "predict number")
      ),
      lines=list(
        lwd=2, col=c("darkred", "darkblue")
      )
    )
  )
  return(profit_plot)
}

```

```{r}
# 関数をtickerごとに繰り返す
# リスト形式で返される
out.plot <- by(data = my.result,
            INDICES = my.result$ticker, 
            FUN = profit_rate_func)

```

# high profit return function

```{r}
profit_last_func <- function(my.result){
  # extract ticker
  my.ticker <- my.result$ticker[1]
  
  # extract date, y, yhat
  my.result %>>% 
    select(yhat) %>>% 
    apply(2, function(i) log(cumprod(1 + i))) %>>% 
    tail(n=1) %>>% 
    (merge(my.ticker, .) -> last_return)
  return(last_return)
}

```

```{r}
# 関数をtickerごとに繰り返す
# リスト形式で返される
out.last <- by(data =my.result,
            INDICES = my.result$ticker, 
            FUN = profit_last_func)

# 縦にマージする
my.result.last <- do.call(rbind, out.last)

# good predict plot num = ??
order(my.result.last$yhat) %>>%
  tail(15) %>% 
  as.vector() %>>%
  my.result.last


```


```{r}
# good predict 
out.plot$FCX
out.plot$EVHC
out.plot$KMI
out.plot$CSX
out.plot$MUR
out.plot$WYNN
out.plot$OKE
out.plot$MLM
out.plot$NRG
out.plot$AKAM
out.plot$NAVI
out.plot$MRO
out.plot$NEM
out.plot$KSU
out.plot$FCX
```




# linear model

```{r}
lm.model <- lm(formula = y ~ yhat, data = my.result)
summary(lm.model)
```

```{r}
# separate by nfor
models <- my.result %>%
  dplyr::group_by(nfor) %>%
  do(ols.model = lm(data = ., formula = y ~ yhat))
knitr::kable(models %>% tidy(ols.model))

```

# trading based on forecasts

strategy is:

buy the stock in end of day t if forecast in t+1 is positive and sell at the end of t+1
short-sell the stock in the end of day t when forecast for t+1 is negative and buy it back in the end of t+1

```{r}
#(yhat>0):return False(0) or True(1)
my.profit <- sum(with(my.result, (yhat>0)*y + (yhat<0)*-y))
print(my.profit)
```

compares to random traiding signals

```{r}
n.sim <- 10000

monkey.ret <- numeric(length = n.sim)
for (i in seq(n.sim)) {
  rnd.vec <- rnorm(length(my.result$y))
  
  monkey.ret[i] <- sum((rnd.vec>0)*my.result$y + (rnd.vec<0)*-my.result$y)
  } 

temp.df <- data.frame(monkey.ret, my.profit)
p <- ggplot(temp.df, aes(monkey.ret)) 
p <- p + geom_histogram()
p <- p + geom_vline(aes(xintercept =  my.profit),size=2)
p <- p + labs(x='Returns from random trading signals')
print(p)

```

